%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Grace Glenn}} & Email : \href{mailto:mglenngrace@gmail.com}{mglenngrace@gmail.com}\\
  \href{https://github.com/mgglenn}{https://github.com/mgglenn} & Mobile : +1-843-697-7111 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Clemson University}{Clemson, SC}
      {B.S. Computer Science - GPA: 3.90}{August 2014 -- May 2018}
      \resumeItemListStart
        \resumeItem{Honors College National Scholars Program}
          {full merit scholarship received by roughly 15 applicants per year}
        \resumeItem{Honors College Global Policy Scholars}
          {travel enrichment program to Strasbourg, France and Berlin, Germany focused on studying public policy.}
        \resumeItem{Recognition / Awards}
          {Departmental Honors, General Honors, Outstanding Junior Award}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Squarespace}{Manhattan, NY}
      {Software Engineer, Machine Learning team}{August 2018 - Present}
      \resumeItemListStart
        \resumeItem{Dataproc for Machine Learning ETLs}
          {Developed framework and processes to use Google's managed Spark resource, Dataproc, for performant
           processing of medium-sized datasets (160 GB)}
        \resumeItem{Kafka}
          {Integrated Kafka message publishing into model training to record statistics and events.}
        \resumeItem{Luigi / GCS }
          {Extended team's Luigi framework to read/write from cloud-hosted (GCS) datasets.}
        \resumeItem{Machine Learning feature modules}
          {Implemented various library modules to apply AWS Facial "Rekognition" detection, language translation, and
           semantic vectorization on image and text inputs.}
      \resumeItemListEnd

    \resumeSubheading
      {Clemson School of Computing}{Clemson, SC}
      {Research and Teaching Assistant}{January 2017 - May 2018}
     \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning}
          {Research through machine learning and data science techniques to develop filters for more relevant social
           media content on political events, including training specialized fastText Vectors and PLDA analysis.}
        \resumeItem{Teaching Assistant - Introduction to C Programming}
          {Teaching Assistant to two lab sections per semester. Responsible for constructing lectures on lab material,
           writing scripts to grade labs, and helping students during office hours.}
     \resumeItemListEnd

    \resumeSubheading
      {Squarespace}{Manhattan, NY}
      {Machine Learning Intern}{June 2017 - August 2017}
     \resumeItemListStart
        \resumeItem{Domain Search Personalization}
          {Developed model to recommend personalized top level domains (TLDs) for a given search. Model made more
           relevant recommendations 3,500\% more often than the company’s former personalization service. Still in use.}
        \resumeItem{Domain Name Generation}
          {Developed model to generate plausible domain name variations for a given domain name search during  hackweek.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Research Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Senior Thesis on Query Expansion}
      {Research with Clemson School of Computing to construct and analyze content topics from Twitter, in order
     to filter more relevant documents (tweets) for political events.}
    \resumeSubItem{Collective Action Modeling (UMass-Amherst R.E.U. 2016)}
      {Modeled group problem-solving to simulate problem-solving strategies through decision trees
      and kernel density estimators, based on real human game-play datasets from University of Pennsylvania.}
    \resumeSubItem{Website Page Recommendation}
      {Prototyped page-recommendation model with custom embedding layer to rank candidate website pages
      (menu, contact, about, etc) for a given text input (e.g., "cafe website").}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, R, C/C++, Java}
    }
    \item{
      \textbf{Technologies}{: Kubernetes, Docker, AWS (S3, DynamoDB), Kafka, GCP (GCE, GCS, Dataproc)}
      \hfill
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
